Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-07-21 manuscript_BMB.tex
added declarations

\title{Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model
\thanks{Grants or other notes
about the article that should go on the front page should be
placed here. General acknowledgments should be placed at the end of the article.}
}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{abstract}
\input{abstract.tex}
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.

>>>>

\title{Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model
% \thanks{Grants or other notes
% about the article that should go on the front page should be
% placed here. General acknowledgments should be placed at the end of the article.}
}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{abstract}
\input{abstract.tex}
\keywords{Epidemiology \and Infectious disease \and SARS-CoV-2 \and COVID-19 \and Reproductive number \and Testing and isolation}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

% \begin{acknowledgements}
% If you'd like to thank anyone, place your comments here
% and remove the percent signs.
% \end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
\section*{Declarations}

\section*{Funding}

DJDE, JD, and BMB were funded by the Natural Sciences and Engineering
Research Council of Canada, the Michael G. DeGroote Institute for Infectious
Disease Research at McMaster University, and the Public Health Agency of
Canada.

\section*{Conflict of interest}

The authors declare that they have no conflict of interest.

\section*{Availability of data and material}

Not applicable.

\section*{Code availability}

Source code required to reproduce all analyses presented in this study are available at https://github.com/aligharouni/SIRmodel.
